% preemble
\documentclass[a4paper,margin=1in]{article}
\usepackage[margin=1in]{geometry}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{lipsum}

\begin{landscape}
\title{Python}
\author{
By : Ravish Ranjan \\
Roll no. 45 \\
Affiliation : Dept. of Computer Science\\
Course : Masters of Computer Science
}
% actual document start
\end{landscape}
\begin{document}
\maketitle

\newpage
\begin{center}
    \Huge{\textit{INTRODUCTION}}
\end{center}
{\LARGE LaTeX plays a \textbf{crucial role} in academic writing by enabling researchers to produce
\textit{highly structured} and professionally formatted documents with ease.\newline Its ability to handle
complex elements such as mathematical equations, citations, bibliographies, and figures makes it\newline
an \underline{indispensable tool} for scholars across disciplines.\newline Unlike conventional word
processors, {\small LaTeX emphasizes content over appearance}, allowing writers to focus on the
logical flow of ideas rather than manual formatting. Furthermore, \newlinw {\Huge its precision and
consistency ensure publication-ready output}, making it the preferred choice for theses,
research papers, and technical reports worldwide.}
\newline
{\Huge{
\begin{flushleft}
\textbf{This text is left aligned.}
\end{flushleft}

\begin{center}
{\it This text is centered.}
\end{center}

\begin{flushright}
{\underline {This text is right aligned.}}
\end{flushright}

This text is Justified by default in Latex
}}

\newpage

\section{This is First Section}
\subsection{\hspace{2em}This is first subsection}
\subsubsection{\hspace{4em}This is first subsub section}
\subsection{\hspace{2em}This is second subsection}
\subsubsection{\hspace{4em}This is second subsub section}

\section{This is second section}
\subsection{\hspace{2em}This is third sub section}
\subsubsection{\hspace{4em}This is third subsub section}
\subsection{\hspace{2em}This is fouth sub section}
\subsubsection{\hspace{4em}This is fourth subsub section}

\end{document}
% document end